### 2024-01-30 Paper/main.tex
Adapt plots where mixed all is present
make changes in paper

\section{Results}
\label{Results}
A mixed model was developed by training the model with images of filesizes 5, 10, 17, 25 and 32. This resulted in 4500 images (512x512) for each codec. The considered dataset has only 900 images. To compare the filesize models with the mixed model, the filesize models need the same amount of input images as the mixed model. Therefore, each image of the dataset was cropped into five images to get an amount of 4500 images for the training and testing.

@@

\section{Performance}
For the classification each model was evaluated with each filesize. The result is represented in the figure \ref{fig: acc_comparison}.

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_filtered.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_withoutMixed.pgf}}
	\caption{Accuracy Comparison}
	\label{fig: acc_comparison}
\end{figure}

\noindent
The self trained model was trained with the filesizes 5, 10, 17, 25 and 32 on all 10 codecs. This leads to 4000 images for each codec per epoch. As one can see in figure \ref{fig: acc_comparison} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.

@@

\noindent
An assumtion was that the mixed model would lead to the best result because of considering different filesizes for the model. As the figure \ref{fig: acc_comparison} shows, almost every small filesize model has a better performance than the mixed model.

\noindent
For classifying images with the given filesizes the model trained with 40kB would lead to the best result. However, for smaller filesize images (\textless 50kB) the model trained with 32kB images would be the right choice because of the bigger accuracy for 5kB images.

>>>>

\section{Results}
\label{Results}
A mixed model was developed by training the model with images of filesizes 5, 10, 17, 25 and 32. This resulted in 4500 images (512x512) for each codec. The considered dataset has only 900 images. To compare the filesize models with the mixed model, the filesize models need the same amount of input images as the mixed model. Therefore, each image of the dataset was cropped into five images to get an amount of 4500 images for the training and testing.
For the purpose of comparison, an additional model was trained using images all available filesizes 5, 10, 17, 25, 32, 40, 50, 60, 75 and 100. This particular model utilized 9000 images during the training phase.

@@

\section{Performance}
For the classification each model was evaluated with each filesize. The result is represented in the figure \ref{fig: acc_comparison all}.

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison.pgf}}
	\caption{Accuracy Comparison All Models}
	\label{fig: acc_comparison all}
\end{figure}

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_filtered.pgf}}
	\caption{Accuracy Comparison Subset of Models}
	\label{fig: acc_comparison filtered}
\end{figure}

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/accuracy/accuracy_comparison_withoutMixed.pgf}}
	\caption{Accuracy Comparison of Filesize Models}
	\label{fig: acc_comparison filesize}
\end{figure}

\noindent
The self trained model was trained with the filesizes 5, 10, 17, 25 and 32 on all 10 codecs. This leads to 4000 images for each codec per epoch. As one can see in figure \ref{fig: acc_comparison all} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.

@@

\noindent
An assumption was that the mixed model would lead to the best result because of considering different filesizes for the model. This assumption got proven by the mixed pre trained model (5-100), shown in the figure \ref{fig:loss_comparison_filesize_10}.
